SDR enhancement by clouds

### 2024-03-19 article/article.Rmd
Commit 2024-03-19 09:11

We have computed the daily trend of the mean over irradiance of CE (Figure\ \ref{fig:CEmeanDaily}), using

.... cite arima lag ....

@@

We observe an increase of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate],3)`\pm
`r round(dailyCE[var == "GLB_diff.mean", Tmod_Std..Error],3)`\,W/m^2$
on the mean over irradiance.

>>>>

We computed the daily trend of the mean over irradiance of CE (Figure\
\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
using the 'maximum likelihood' fitting method [@Gardner1980; @Jones1980] by
implementing the function 'arima' from the library 'stats' of the R programming
language [@RCT2023]. The trends were reported together with the $2\sigma$ error.
We observe an increase of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate],3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error],3)`\,W/m^2$
on the mean over irradiance.

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one minute measurements.

### 2024-03-19 article/article.tex
Commit 2024-03-19 09:11

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-03-17}

@@

We have computed the daily trend of the mean over irradiance of CE (Figure~\ref{fig:CEmeanDaily}), using

\ldots. cite arima lag \ldots.

@@

We observe an increase of
\(0.216\pm 0.041\,W/m^2\)
on the mean over irradiance.

@@

@@

@@

>>>>

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-03-19}

@@

We computed the daily trend of the mean over irradiance of CE (Figure\\
\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
using the `maximum likelihood' fitting method (Gardner, Harvey, and Phillips 1980; Jones 1980) by
implementing the function `arima' from the library `stats' of the R programming
language (R Core Team 2023). The trends were reported together with the \(2\sigma\) error.
We observe an increase of
\(0.216\pm 0.083\,W/m^2\)
on the mean over irradiance.

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one minute measurements.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Gardner1980}{}}%
Gardner, G., A. C. Harvey, and G. D. A. Phillips. 1980. {``Algorithm {AS} 154: An Algorithm for Exact Maximum Likelihood Estimation of Autoregressive-Moving Average Models by Means of Kalman Filtering.''} \emph{Applied Statistics} 29 (3): 311. \url{https://doi.org/10.2307/2346910}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Jones1980}{}}%
Jones, Richard H. 1980. {``Maximum Likelihood Fitting of {ARMA} Models to Time Series with Missing Observations.''} \emph{Technometrics} 22 (3): 389--95. \url{https://doi.org/10.1080/00401706.1980.10486171}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-RCT2023}{}}%
R Core Team. 2023. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
